---
title: "SRT411A0"
author: "Christopher Pawlaczek"
output: html_document
---

GitHub Username: cpawlaczek

  A link to the document we are using: https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf
  
  This is the code and outputs for all 14 ToDos found in "A (very) Short Introduction to R", done for Assignment 0 in SRT411.
  

####ToDo 1) Computing Difference
```{r}
((2019-2013)/22)*100
```

####Todo 2) Variables
```{r}
a = 2019
b = 2013
c = 22
((a-b)/c)*100
```

####Todo 3) Matrices
```{r}
m=c(4,5,8,11)
sum(m)
```

####Todo 4) Rnorm
```{r}
x = rnorm(100)
plot(x)
```

####Todo 5) Sqrt Help
```{r}
help(sqrt)
```

####Todo 6) First Script
```{r}
x = rnorm(100)
plot(x)
```

####Todo 7) More Matrices
```{r}
P = seq(from=31, to=60, by=1)
Q=matrix(data=c(P),ncol=5)
Q
```

####Todo 8) Data Frames
```{r}
x1= rnorm(100)
x2= rnorm(100)
x3= rnorm(100)

t = data.frame(a = c(x1), b = c(x2+x3), c = c(x1+x2+x3))
plot(t)
```

####Todo 9) Graphing
```{r}
x1= rnorm(100)
x2= rnorm(100)
x3= rnorm(100)

t = data.frame(a = c(x1), b = c(x2+x3), c = c(x1+x2+x3))
plot(t)

plot(t$a, type="l", ylim=range(t),
     lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,
      col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,
       col=rgb(0,0,1,0.3))
```

####Todo 10) Reading / Writing
```{r}
d = data.frame(a = c(1,2,4,8,16,32), g = c(2,4,8,16,32,64), x = c(3,6,12,24,48,96))
write.table(d, file="tst1.txt", row.names=FALSE)
d2 = read.table(file="tst1.txt", header=TRUE)
d2$g=d2$g*5
write.table(d2, file="tst2.txt", row.names=FALSE)
```

####Todo 11) Not Available Data
```{r}
vectest = c(rnorm(100))
mean((sqrt(vectest)))
##NaNs produced
```

####Todo 12) Dates
```{r}
date1=strptime( c("20190315", "20191205", "20191115"), format="%Y%m%d")
present1=(c(1,2,3))
plot(date1, present1)
```

####Todo 13) For-Loop
```{r}
sec13 = seq(from=1, to=100)
vec13 = c()
for (i in 1:100)
{
  if( i < 5 )
  {vec13[i] = sec13[i] * 10}
  else if(i > 90)
  {vec13[i] = sec13[i] * 10}
  else 
  {vec13[i] = sec13[i] * 0.1}
}
print(vec13)
```

####Todo 14) Function Loop
```{r}
fun2 = function(arg5)
{
  sec13 = seq(from=1, to=arg5)
  vec13 = c()
  for (i in 1:arg5)
  {
    if( i < 5 )
    {vec13[i] = sec13[i] * 10}
    else if(i > 90)
    {vec13[i] = sec13[i] * 10}
    else 
    {vec13[i] = sec13[i] * 0.1}
  }
  print(vec13)
}
```

